\begin{frame}

\frametitle{Reading Material}

\footnotesize

Academic:

\begin{itemize}

\item Tom Mens and Tom Tourw\'e. 2004. \emph{A Survey of Software Refactoring}.
IEEE Transactions on Software Engineering 30 (2), 2004, 126--139.

\end{itemize}

Web:

\begin{itemize}

\item Shvets Group, et al. \url{https://refactoring.guru/}

\begin{itemize}

\item \footnotesize \url{https://refactoring.guru/catalog/}.

\end{itemize}

\item Martin Fowler, \url{http://refactoring.com/}

\begin{itemize}

\item \footnotesize \url{http://refactoring.com/catalog/}.

\end{itemize}

\end{itemize}

Light reading:

\begin{itemize}

\item \texttt{oleks} \& \texttt{br0ns}. \emph{Unix-Like Data Processing
Utilities}. 2015. \url{http://atu15.onlineta.org/unix-like-data-processing.pdf}

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Video Material}

\footnotesize

\begin{itemize}

\item Maria Letizia Jaccheri. \emph{Configuration Management}. \\ Norwegian
University of Science and Technology, 2013. \url{https://youtu.be/i2E1VDjmrXo}

\item Bob Aiello. \emph{What Project Managers Need to Know About Configuration
Management}. NYC PMI, 2012. \url{https://youtu.be/NsQZNqVpb8Y}

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Summer Reading}

\footnotesize

\begin{itemize}

\item Bob Aiello. \emph{Configuration Management Best Practices: Practical
Methods that Work in the Real World}. Addison-Wesley, 2011.

\item Ben Moseley and Peter Marks. \emph{Out of the Tar Pit}. \\ Software
Practice Advancement, 2006.

\end{itemize}

\end{frame}
